### 2014-07-30 paper/paper.tex
Templated the full table 1 and wrote a set of tests for the table in the makefile
Fixed some mistakes in the code and wrote a single make target to make one table col

@@

\begin{table}[H]
    \begin{center}
    \begin{tabular}{|c|c|r|r|r|r|}
        \hline
        Description & Stopwords & Run 1 & Run 2 & Run 3 & $\mu$ F\\
        \hline
        MaxEnt      & Yes       & 0.0   & 0.0   & 0     & 0 \\
        \dots       & No        & 0.0   & 0.0   & 0     & 0 \\
        Naive Bayes & Yes       & 0.0   & 0.0   & 0     & 0 \\
        \dots       & No        & 0.0   & 0.0   & 0     & 0 \\
        \hline
    \end{tabular}
    \end{center}
    \caption{Results of variations on feature selection and training. Sorted by
        average F-score.}
    \label{table:results}
\end{table}

>>>>

The dataset for the task consists of 6225 labelled Tweets. 36.66\% of the
corpus has `positive' label, 14.04\% has a `negative' label, 49.30\% has a
label that conveys neutral sentiment. This neutral label is one of `neutral',
`objective', or `objective-OR-neutral'.

@@

\begin{table}[H]
    \begin{center}
    \begin{tabular}{|c|c|c|c|r|r|r|r|}
        \hline
        Description & Stopwords & Uncommon  & Normalize & Run 1 & Run 2 & Run 3 & $\mu F$\\
        \hline
        MaxEnt      & Yes       & Yes       & Yes       & 50.97 & 0.0   & 0.0   & 0.0 \\
        \dots       & Yes       & Yes       & No        & 56.21 & 0.0   & 0.0   & 0.0 \\
        \dots       & Yes       & No        & Yes       & 51.25 & 0.0   & 0.0   & 0.0 \\
        \dots       & Yes       & No        & No        & 54.44 & 0.0   & 0.0   & 0.0 \\
        \dots       & No        & Yes       & Yes       & 50.71 & 0.0   & 0.0   & 0.0 \\
        \dots       & No        & Yes       & No        & 51.03 & 0.0   & 0.0   & 0.0 \\
        \dots       & No        & No        & Yes       & 50.41 & 0.0   & 0.0   & 0.0 \\
        \dots       & No        & No        & No        & 51.56 & 0.0   & 0.0   & 0.0 \\
        Naive Bayes & Yes       & Yes       & Yes       & 50.27 & 0.0   & 0.0   & 0.0 \\
        \dots       & Yes       & Yes       & No        & 50.27 & 0.0   & 0.0   & 0.0 \\
        \dots       & Yes       & No        & Yes       & 50.85 & 0.0   & 0.0   & 0.0 \\
        \dots       & Yes       & No        & No        & 52.12 & 0.0   & 0.0   & 0.0 \\
        \dots       & No        & Yes       & Yes       & 47.19 & 0.0   & 0.0   & 0.0 \\
        \dots       & No        & Yes       & No        & 50.56 & 0.0   & 0.0   & 0.0 \\
        \dots       & No        & No        & Yes       & 49.82 & 0.0   & 0.0   & 0.0 \\
        \dots       & No        & No        & No        & 52.15 & 0.0   & 0.0   & 0.0 \\
        \hline
    \end{tabular}
    \end{center}
    \caption{Results of variations on feature selection and training. Sorted by
        average F-score.}
    \label{table:results}
\end{table}

%TODO write about the number of features
